Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-22 manuscript/response_to_reviews.Rmd

f. Line 210: I am confused by the statement that of the 39762 records in ForC v3.0, 11923 were included in this study. Previously (lines 135-149), the authors described creating "ForC-simplified" with 17349 records. Clarify the difference between ForC-simplified and ForC v3.0.

**It appears that reference to ForC-simplified (essentially an automatically generated rearrangement of ForC that is purged of duplicates and organized for easy analysis) makes the process more confusing, and isn't necessary, so we eliminated mention of it.**

g. Line 212: The authors refer to ForC, where in the previous sentence they referred to ForC v3.0, and previously used ForC-simplified. Clarify what database is used in the analyses.

**As in the response above, we have eliminated unnecessary/confusing mention of ForC-simplified. The version used is ForC v3.0 (to be released with DOI upon acceptance of this manuscript). We do not feel it is necessary to state the version number every time ForC is mentioned.**

@@

**Thank you.**

However, I also found that many aspects of the paper gave me considerable pause.

First, the paper covers an awful lot of ground. It strikes me that each of the three research questions (bottom of page 4) could easily motivate an entire paper on their own. By attempting to address all three in one (relatively short) manuscript, it is not possible to discuss in any detail the mechanisms and processes that determine the results. There are no process-oriented hypotheses or frameworks against which the results are evaluated.

**We agree that this covers a lot of ground, which corresponds with our vision of producing a comprehensive synthesis of broad trends. We envision that smaller questions can (and hopefully will) be broken off for more detailed analysis in the future.**

**At the same time, we agreed that the manuscript could be improved with more of a conceptual framework. To improve in this area, we have expanded and reorganized the introduction into four sub-sections ("Forests in the global C cycle: current and future", "Evolution of forest C cycle research", "Biome differences", and "Age trends and their variation across biomes"). The latter three sections are mostly or entirely new relative to the previous version, and briefly review the development and current status of the science on each topic. We have also added a schematic figure (Fig. 1) to summarize current understanding of each topic and help with conceptual framing of the review. We also shifted emphasis more towards the ecological questions (trends across biomes and with age), while retaining (with less emphasis) the analysis of database representativeness.**

@@

For example, concerning expectations about how various C cycles and pools vary with stand age? There is a fairly extensive literature on this topic … Odum’s classic paper on the topic (“The Strategy of Ecosystem Development, 1969) has been cited thousands of times. But this literature is not referenced or cited in the current manuscript. Odum’s hypothesis suggests that NEP (arguably the most important flux, at least from a climate mitigation perspective) should increase initially with stand age and then eventually decrease as forests continue to mature. However, this framework/literature is not referenced, and the way the results are presented make it difficult to understand whether those expectations were borne out in the data. On that note, I didn’t understand why the authors chose to show flux trends explicitly as a function of age up to 100 years (Figure 6), but then group all the forests >100 years old into a single “bar). Why not plot the mature forests explicitly on the flux versus age axis? This would allow a clearer assessment of whether flux trends with age are really linear.  It would also help the reader understand better one of the most striking results from this manuscript: that NEP of mature forests is indistinguishable across biomes. The authors describe this as unsurprising, but I think it is a bit unexpected, especially given the results of some of the more synthetic work from FLUXNET (e.g. Luyssaert et al. 2007). The authors explain this result in a couple of sentences (Page 25, lines 22-26), speculating that the result is driver by “moderate disturbances” or “disequilibrium of Rsoil relative to C inputs). A deeper dive into the results, combined with some mechanistic grounding, might reveal to what extent this result represents a climate-age interaction that is predicted from the existing theory.

**We greatly appreciated the suggestion to engage with Odum's framework. We now cite and discuss @odum_strategy_1969 in the introduction, and designed the age trends portion of the schematic figure to correspond to Odum's classic Fig. 1 (updated with more details and current terminology).**

@@

**Regarding the question of showing flux trends as a function of age beyond 100 years, this unfortunately doesn't make sense within the context of the database because tropical forests can rarely be aged beyond 100 years (if that). This is because tropical trees rarely form annual rings, which are used to age (older) extratropical forests. It would not make sense to treat tropical and extra-tropical forests differently.**

**Regarding the NEP result for mature forests, we agree that a better conceptual framework (now implemented) should help set the stage for explaining this result.  We have modified the discussion paragraph on this to cite the schematic figure and also to note that this result does agree with @luyssaert_co2_2007 (although that study did not standardize for age). The paragraph now reads as follows:**

**"The notable exception to the pattern of fluxes decreasing from tropical to boreal regions is $NEP$, which showed no significant differences across biomes (Fig. 6f). Unlike the other C flux variables, $NEP$ does not characterize the rate at which C cycles through the ecosystem, but is the balance between C sequestration ($GPP$) and respiratory losses ($R_{eco}$) and represents net CO~2~ sequestration (or release) by the ecosystem (Fig. 1). $NEP$ tends to be relatively small in mature forest stands (discussed further below), which accumulate carbon slowly relative to younger stands, if at all [@luyssaert_old-growth_2008; @amiro_ecosystem_2010; @besnard_quantifying_2018]. It is therefore unsurprising that there are no pronounced differences across biomes [in agreement with @luyssaert_co2_2007], suggesting that variation in $NEP$ of mature forests is controlled less by climate and more by other factors including moderate disturbances [@curtis_forest_2018] or disequilibrium of $R_{soil}$ relative to C inputs [e.g., in peatlands where anoxic conditions inhibit decomposition; @wilson_stability_2016]."**

@@

Finally, I wondered about the interacting effects of changing climate (rising CO2, warming temperatures) and stand age, especially in determining trends in the pools. Mature forests will have experienced a much wider range of climate conditions than younger stands. How does this complicate the comparison of live biomass across forest of different age?

**This is an excellent question, and one that is of great interest to the lead author [e.g., @andersonteixeira_altered_2013]; however, we think it is unlikely to have much influence at this relatively coarse scale of analysis, especially given that much of the data in ForC was collected in the 20th century. Sorting this out would require carefully designed studies, and probably would not be possible using ForC data at this point.**

### 2021-01-22 manuscript/ERL_global_C_review.Rmd
worked on response to reviews

The notable exception to the pattern of fluxes decreasing from tropical to boreal regions is $NEP$ (Fig. `r flux_age_trends`), which showed no significant differences across biomes.
Unlike the other C flux variables, $NEP$ does not characterize the rate at which C cycles through the ecosystem, but is the balance between C sequestration ($GPP$) and respiratory losses ($R_{eco}$) and represents net CO~2~ sequestration (or release) by the ecosystem.
$NEP$ tends to be relatively small in mature forest stands (discussed further below), which accumulate carbon slowly relative to younger stands, if at all [@luyssaert_old-growth_2008; @amiro_ecosystem_2010; @besnard_quantifying_2018].
It is therefore unsurprising that there are no pronounced differences across biomes, suggesting that variation in $NEP$ of mature forests is controlled less by climate and more by other factors including moderate disturbances [@curtis_forest_2018] or disequilibrium of $R_{soil}$ relative to C inputs [e.g., in peatlands where anoxic conditions inhibit decomposition; @wilson_stability_2016].

>>>>

The notable exception to the pattern of fluxes decreasing from tropical to boreal regions is $NEP$, which showed no significant differences across biomes (Fig. `r flux_age_trends`f).
Unlike the other C flux variables, $NEP$ does not characterize the rate at which C cycles through the ecosystem, but is the balance between C sequestration ($GPP$) and respiratory losses ($R_{eco}$) and represents net CO~2~ sequestration (or release) by the ecosystem (Fig. `r schematic`).
$NEP$ tends to be relatively small in mature forest stands (discussed further below), which accumulate carbon slowly relative to younger stands, if at all [@luyssaert_old-growth_2008; @amiro_ecosystem_2010; @besnard_quantifying_2018].
It is therefore unsurprising that there are no pronounced differences across biomes [in agreement with @luyssaert_co2_2007], suggesting that variation in $NEP$ of mature forests is controlled less by climate and more by other factors including moderate disturbances [@curtis_forest_2018] or disequilibrium of $R_{soil}$ relative to C inputs [e.g., in peatlands where anoxic conditions inhibit decomposition; @wilson_stability_2016].
